Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2016-11-18 Draft_1.tex
Added to NLP section, only discussion of solved issues required

\documentclass[twocolumn]{article}
\usepackage{cite}

@@

        \Large
        Word Count - 3000\\
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        20 November 2016

@@

\subsection{Natural Language Processing}
\label{sec:NLP}
The problem of natural language processing or, more specifically, input text analysis, has traditionally be broken down into smaller sub-problems\cite{NLPHandbook}:
\begin{itemize}
	\item Text Preprocessing
	\item Lexical Analysis
	\item Syntactic Parsing
	\item Semantic Analysis
\end{itemize}
The subsequent subsections will discuss each of these in more detail.

@@

\subsubsection{Semantic Analysis}
\label{sec:SemanticAnalysis}
Semantics .

>>>>

\documentclass[twocolumn]{article}
\usepackage{cite}
\usepackage{hyperref}

@@

        \Large
        Word Count - PLACEHOLDER\\
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        20 November 2016

@@

%--------------------- NLP

\subsection{Natural Language Processing}
\label{sec:NLP}
The study of natural language processing aims to allow a computer to understand natural language, and formulate a relevant response based upon its input. Within this, the problem of input text analysis has traditionally be broken down into smaller sub-problems\cite{NLPHandbook}:
\begin{itemize}
	\item Text Preprocessing
	\item Lexical Analysis
	\item Syntactic Parsing
	\item Semantic Analysis
\end{itemize}
The subsequent subsections will discuss each of these in more detail.

@@

\subsubsection{Semantic Analysis}
\label{sec:SemanticAnalysis}
The semantics of a sentence, is the meaning given by it's tokens \cite{SemanticAnalysisAPracticalIntro}. Further detail of semantic analysis can be found in the \hyperref[sec:PrevWork]{Previous Work section}.

%------------ Memory Models
\subsection{Memory Models}
\label{sec:MemModels}

%------------ PREVIOUS WORK
\subsection{Previous Work}
\label{sec:PrevWork}
